\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-08 reports/paper.tex
update paper

The memory-mapped accelerator can operate in two different ways: i) automatic
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{media/ecb_speedup}
  \caption{Speedup using different accelerator configurations in ECB mode.}
  \label{fig:ecbspeedup}
\end{figure}

>>>>

The memory-mapped accelerator can operate in two different ways: i) automatic
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive or single operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{media/ecb_speedup}
  \caption{Speedup using different accelerator configurations in ECB mode.
    Values are relative to the in-order pure software implementation.}
  \label{fig:ecbspeedup}
\end{figure}

@@

\begin{itemize}
\item Pure software: ECB and CBC mode
\item MMIO accelerator, single: ECB and CBC mode
\item MMIO accelerator, automatic: ECB mode
\item Tightly-coupled accelerator: ECB and CBC mode
\item Hybrid accelerator: ECB mode
\end{itemize}

Usage of the MMIO accelerator in automatic mode highlights the characteristics
of a heterogeneous system that is computation-bound, whereas usage of it in the
single mode intends to model a communication-bound architecture.

The reference software implementation is used as a baseline,
Figures~\ref{fig:ecbspeedup},\ref{fig:cbcspeedup} show the relative speedup
(computed from the total cycle count for each of the benchmarks) of alternative
implementations using accelerators or a 2-way BOOM core for encryption in ECB
and CBC mode, respectively.

% TODO small interpretation paragraph here

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{media/scatter_results}
  \caption{Distribution of all benchmark results with respect to both total
    number of instructions retired by processor and total number of cycles
    required to complete operations.}
  \label{fig:scatter}
\end{figure}
